Genome-wide changes in expression during inflorescence architecture development

### 2015-08-17 ms.Rmd
tried using lrt result for mfuzz but it doesn't work

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  word_document:
    fig_caption: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("cairo_pdf"),
               fig.width=6.614,
               fig.height=6.614,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

@@

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=4.40933}
print(f_mfuzzClusters)
```

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: svg
  word_document:
    fig_caption: yes
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/test.bib
---

@@

knitr::opts_chunk$set(fig.path='figures/',
               cache.path='cache/',
               dev=c("svg", "cairo_pdf"),
               fig.width=3.150,
               fig.height=6.3,
               fig.align = 'center',
               dpi=300,
               fig.show='hold',
               cache=FALSE,
               echo=FALSE,
               results="hide",
               message=FALSE,
               warning=FALSE)

@@

```{r lmdFigure}
figCount <- incCount(figCount, "f_lmdFigure")
f_lmdFigure <- "data/lmdFigure.pdf"
```

@@

![`r I(pasteLabel("Figure", figCount, "f_lmdFigure"))`](data/lmdFigure.pdf)

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=6.3, cache = TRUE}
print(f_mfuzzClusters)
```
